ACNP 2024 MS ANXIETY

### 2024-09-06 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL_updated_figs.Rmd
added cohen's d and figures

# Create the ggplot
promis_with_post_op_mental_vs_physical <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, color = health_variable)) +
  geom_line(size = 1.2) +
  scale_x_continuous(breaks = c(0, 1, 2),  # Keep numeric values on x-axis
                     labels = c("MS+noA", "MS+mildA", "MS+severeA")) +  # Set custom labels for each numeric value
  scale_y_continuous(limits = c(0, 7)) +
  geom_errorbar(aes(ymin = mean_promis_score - sem_promis_score, ymax = mean_promis_score + sem_promis_score), width = 0.2, size = 0.8)  +
  theme(
        axis.text.y = element_text(size=12, colour = "black"),
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size=12, colour = "black"),
        legend.title = element_blank(),
        legend.position = c(0.8, 0.95),  # Move legend to upper right of plot area (0.9, 0.9 corresponds to top-right)
        legend.background = element_rect(fill = "white"),  # Set legend background to white
        legend.key = element_rect(fill = "white", color = "white"),  # Set legend key background to white
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white")) +
  labs(y= "Mean PROMIS Score") +
  scale_color_manual(values = custom_colors_simple, breaks = desired_order)

promis_with_post_op_mental_vs_physical
#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/promis_with_post_op_mental_vs_physical.pdf"))
  promis_with_post_op_mental_vs_physical
dev.off()

@@

#looking at anxiety_dose = 2 only, 0.22 -> sample size too small

mental_vs_physical_health_t <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
mental_vs_physical_health_t

#physical health, sick vs healthy - t = 2.0048, df = 8.6555, p-value = 0.07722
physical_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
physical_health_t_sick_vs_healthy

#mental health, sick vs healthy - t = 3.6838, df = 8.1324, p-value = 0.006011
mental_health_t_sick_vs_healthy <- t.test(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
mental_health_t_sick_vs_healthy

@@

@@

#### Plots 
#####Uncinate R,L,mean Prop
```{r plots_uncinate}
  #proportion injured over R Uncinate prop

#n=372
df_mean_UF_mean_by_anxiety_severity <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
  mutate(mean_UF_prop = mean_UF_prop*100) %>%
  group_by(anxiety_severity) %>%
  summarise(mean_UF_mean = round(mean(mean_UF_prop , na.rm = TRUE),0),
            sd_UF = sd(mean_UF_prop, na.rm = TRUE),
            sem_UF = sd(mean_UF_prop, na.rm = TRUE) / sqrt(n())) %>%
  mutate(anxiety_severity = factor(anxiety_severity, levels = unique(anxiety_severity))) %>%
  ungroup()

prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_mean_UF_mean_by_anxiety_severity, aes(x=anxiety_severity, y=mean_UF_mean, fill=anxiety_severity)) +
  geom_bar(stat="identity", width = .6) +  
  geom_errorbar(aes(ymin = mean_UF_mean - sem_UF, ymax = mean_UF_mean + sem_UF), width = 0.2, size = 0.8)  +
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
  ylim(0,45)+
  theme(axis.text.x = element_text(size=12, colour = "black"),
        axis.text.y = element_text(size=12, colour = "black"),
        axis.title.y = element_text(size=16, colour = "black"),
        axis.title.x = element_blank(),
        axis.line = element_line(linewidth = 1.5, colour="black"),
        legend.position = "none",
        aspect.ratio = 7/5,
        panel.background = element_rect(colour = "white", fill = "white")) + 
  labs(y = "Percent (%) of Uncinate Injured")
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar

#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_bar.pdf"))
  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar
dev.off()

### try horizontal
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar_horiz <-  ggplot(df_mean_UF_mean_by_anxiety_severity, aes(y=anxiety_severity, x=mean_UF_mean, fill=anxiety_severity)) +
  geom_bar(stat="identity", width = .6) +  
  geom_errorbar(aes(xmin = mean_UF_mean - sem_UF, xmax = mean_UF_mean + sem_UF), width = 0.2, size = 0.8)  +
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
  xlim(0,45)+
  theme(axis.text.x = element_text(size=12, colour = "black"),
        axis.text.y = element_text(size=12, colour = "black"),
        axis.title.x = element_text(size=16, colour = "black"),
        axis.title.y = element_blank(),
        axis.line = element_line(linewidth = 1.5, colour="black"),
        legend.position = "none",
        aspect.ratio = 7/5,
        panel.background = element_rect(colour = "white", fill = "white")) + 
  labs(x = "Percent (%) of Uncinate Injured")
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar_horiz

```
##### Uncinate Violin Plot
```{r uncinate_violin}
#### trying prettier things
df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
  mutate(mean_UF_prop = mean_UF_prop*100)

# Create the plot with narrower violins and error bars
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, fill = anxiety_severity)) +
  geom_violin(width = 0.5, alpha =.5, color = "black", trim = FALSE) +  # Adjust violin width and transparency
  stat_summary(fun = "mean", geom = "crossbar", width = 0.3, color = "black", size = 0.5) +  # Add horizontal lines at means
  #geom_point(position = position_jitter(seed = 1, width = 0.2)) +

#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  ylim(0,100) +
  #geom_errorbar(aes(ymin = mean_UF_prop - sem_UF_prop, ymax = mean_UF_prop + sem_UF_prop), width = 0.2, color = "black") +  # Add error bars
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
  #theme_minimal(base_size = 14) +  # Use a minimal theme with a base font size
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),  # Rotate x-axis labels for better readability
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white"),
    plot.margin = margin(10, 10, 10, 10),  # Add margins around the plot
    aspect.ratio = 5/5
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot

#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_violin.pdf"))
  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
dev.off()

```
##### Geom point
```{r geom_point}
#### trying prettier things
df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
  mutate(mean_UF_prop = mean_UF_prop*100)

# Create the plot with narrower violins, viridis colors, and horizontal lines at means
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_point(position = position_jitter(width=.1, height = 0), size = 2, alpha = 0.8) +  # Add points with jitter using viridis colors
  stat_summary(fun = "mean", geom = "crossbar", width = 0.3, color = "black", size = 0.5) +  # Add horizontal lines at means
  scale_color_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale for points
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),  # X-axis labels
    axis.text.y = element_text(size = 12, colour = "black"),  # Y-axis labels
    axis.title.y = element_text(size = 16, colour = "black"),  # Y-axis title
    axis.title.x = element_blank(),  # Remove X-axis title
    axis.line = element_line(linewidth = 1.5, colour = "black"),  # Axis lines
    legend.position = "none",  # Remove legend
    panel.background = element_rect(colour = "white", fill = "white")  # Background
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")  # Y-axis label

#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/UF_anxiety_severity_dot.pdf"))
  prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
dev.off()

##### Box plot with jitter ND OTHERS
```{r box_jitter}
#### trying prettier things
df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
  mutate(mean_UF_prop = mean_UF_prop*100)

##BOX PLOT WITH JITTER
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.3, outlier.size = 0) +  # Add boxplots with some transparency
  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
  scale_fill_viridis(discrete = TRUE, option = "D") +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

# Display the plot
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
```

##### Box plot no jitter
```{r box_plot_no_jitter}

@@

  #"MS+noA" = "#1F968B",
  #"MS+mildA" = "#39568C",
  #"MS+severeA" = "#482677" 
    #"MS+noA" = "#55C667",
  #"MS+mildA" = "#238A8D",
  #"MS+severeA" = "#404788" 
    #  "MS+noA" = "#404788",
#  "MS+mildA" = "#482677",
#  "MS+severeA" = "#440154" 
  #      "MS+noA" = "#1f968abf",
  #"MS+mildA" = "#33638d",
  #"MS+severeA" = "#482677" 
 #         "MS+noA" = "#29af7f",
#  "MS+mildA" = "#33638d",
#  "MS+severeA" = "#440154" 
            "MS+noA" = "#55c667",
  "MS+mildA" = "#2d708e",
  "MS+severeA" = "#440154" 
 # "MS+mildA" = viridis::viridis(3, option = "C")[2],  # Use green from 'D' for MS+noA
#  "MS+severeA" = viridis::viridis(3, option = "D")[1],  # Use a different color from 'D'
#  "MS+noA" = viridis::viridis(3, option = "D")[2]  # Use the last color from 'D'
)

##### BOX PLOT NO JITTER
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.65, outlier.size = 0) +  # Add boxplots with some transparency
    scale_color_manual(values = custom_colors) +  # Apply custom color scale
  scale_fill_manual(values = custom_colors) +  # Apply custom fill scale
#  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
  #scale_color_viridis(discrete = TRUE, option = "C", direction = -1) +  # Use Viridis color scale
  #scale_fill_viridis(discrete = TRUE, option = "C", direction = -1) +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    aspect.ratio = 7/6,
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

@@

prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_horiz <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(y = anxiety_severity, x = mean_UF_prop, color = anxiety_severity)) +
  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.65, outlier.size = 0) +  # Add boxplots with some transparency
#  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
  scale_color_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.x = element_text(size = 16, colour = "black"),
    axis.title.y = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    aspect.ratio = 5/6,
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(x = "Percent (%) of Uncinate Injured")
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_horiz

@@

###### dot plot
```{r dot_plot_and_others}

df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
  mutate(mean_UF_prop = mean_UF_prop*100)

##plot
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_point(position = position_jitter(width = 0.2, height = 0), size = 2, alpha = 0.8) +  # Individual data points with jitter
  stat_summary(fun = "mean", geom = "point", size = 4, shape = 21, fill = "black") +  # Mean points
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, color = "black") +  # Confidence intervals
  scale_color_viridis(discrete = TRUE, option = "D") +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

### bar with error
summary_stats <- df_disease_burden_unc_and_anx_net_collapsed_variables %>%
  group_by(anxiety_severity) %>%
  summarize(mean_UF_prop = mean(mean_UF_prop, na.rm = TRUE),
            sd_UF_prop = sd(mean_UF_prop, na.rm = TRUE),
            n = n(),
            se_UF_prop = sd_UF_prop / sqrt(n))

prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(summary_stats, aes(y = anxiety_severity, x = mean_UF_prop, fill = anxiety_severity)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.7) +  # Bar plot
  geom_errorbar(aes(xmin = mean_UF_prop - se_UF_prop, xmax = mean_UF_prop + se_UF_prop), width = 0.2) +  # Error bars
  scale_fill_viridis(discrete = TRUE, option = "D") +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
#    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.y = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(x = "Percent (%) of Uncinate Injured")

# Display the plot
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
```

>>>>

# Create the ggplot
promis_with_post_op_mental_vs_physical <- ggplot(df_for_promis_plot_mental_vs_physical_healthy, aes(x = anxiety_dose, y = mean_promis_score, color = health_variable)) +
  geom_line(size = 1.2) +
  scale_x_continuous(breaks = c(0, 1, 2),  # Keep numeric values on x-axis
                     labels = c("MS+noA", "MS+mildA", "MS+severeA")) +  # Set custom labels for each numeric value
  scale_y_continuous(limits = c(0, 7)) +
  geom_errorbar(aes(ymin = mean_promis_score - sem_promis_score, ymax = mean_promis_score + sem_promis_score), width = 0.2, size = 0.8)  +
  theme(
        axis.text.y = element_text(size=12, colour = "black"),
        axis.title.y = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size=12, colour = "black"),
        legend.title = element_blank(),
        legend.position = c(0.8, 0.95),  # Move legend to upper right of plot area (0.9, 0.9 corresponds to top-right)
        legend.background = element_rect(fill = "white"),  # Set legend background to white
        legend.key = element_rect(fill = "white", color = "white"),  # Set legend key background to white
        legend.text = element_text(size=10),
        aspect.ratio=7/5,
        panel.background = element_rect(colour = "white", fill = "white")) +
  labs(y= "Mean PROMIS Score") +
  scale_color_manual(values = custom_colors_simple, breaks = desired_order)

promis_with_post_op_mental_vs_physical

#save pdf
pdf(file=paste0(homedir, "/results/Figures_for_msanxiety_paper/promis_with_post_op_mental_vs_physical.pdf"))
  promis_with_post_op_mental_vs_physical
dev.off()

@@

@@

#post-hoc pairwise t-tests
#looking at anxiety_dose = 0, 1 and 2

# dose 2, "(T = 2.88, df = 6, P = 0.028, Cohen's d =  -0.69, Effect size = medium)"
physical_vs_mental_health_anxiety_severeA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "T")
print(physical_vs_mental_health_anxiety_severeA[1])

#dose 1, "(T = 2.97, df = 44, P = 0.005, Cohen's d =  -0.38, Effect size = small)"

physical_vs_mental_health_anxiety_mildA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==1], paired = "T")
print(physical_vs_mental_health_anxiety_mildA[1])

#dose 0, "(T = 0.68, df = 11, P = 0.513, Cohen's d =  -0.22, Effect size = small)"

physical_vs_mental_health_anxiety_noA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], paired = "T")
print(physical_vs_mental_health_anxiety_noA[1])

###physical health, sick vs healthy - "(T = 2.00, df = 8.66, P = 0.077, Cohen's d =  -1.01, Effect size = large)"

physical_health_noAvsSevereA <- t_and_cohen_d(sample_1 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], sample_2 = df_for_promis_plot_mental_vs_physical_healthy_test$physical_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired = "F")
print(physical_health_noAvsSevereA[1])

###mental health, sick vs healthy - (T = 3.68, df = 8.13, P = 0.006, Cohen's d =  -1.87, Effect size = large)
mental_health_noAvsSevereA <- t_and_cohen_d(df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==0], df_for_promis_plot_mental_vs_physical_healthy_test$mental_health_score[df_for_promis_plot_mental_vs_physical_healthy_test$anxiety_dose ==2], paired=F)
print(mental_health_noAvsSevereA[1])

#construct df of p values
p_and_cohen_values <- t(data.frame(rbind(c(physical_vs_mental_health_anxiety_noA[2],
                         physical_vs_mental_health_anxiety_mildA[2],
                         physical_vs_mental_health_anxiety_severeA[2],
                         mental_health_noAvsSevereA[2],
                         physical_health_noAvsSevereA[2]),
                         c(physical_vs_mental_health_anxiety_noA[3],
                         physical_vs_mental_health_anxiety_mildA[3],
                         physical_vs_mental_health_anxiety_severeA[3],
                         mental_health_noAvsSevereA[3],
                         physical_health_noAvsSevereA[3])), 
                         row.names = c("p", "cohen_d")))

#construct vector of names
t_test_names <- c("Physical vs Emotional Functioning MS+noA", 
"Physical vs Emotional Functioning MS+mildA",
"Physical vs Emotional Functioning MS+severeA",
"Emotional Functioning MS+severeA vs MS+noA",
"Physical Functioning MS+severeA vs MS+noA")

rownames(p_and_cohen_values) <- t_test_names

#fdr correct
p_and_cohen_values <- as.data.frame(p_and_cohen_values) %>%
  mutate(fdr = round(p.adjust(p, method = "fdr"),3)) %>%
  mutate(p = as.numeric(p)) %>%
  mutate(cohen_d = as.numeric(cohen_d)) %>%
  relocate(cohen_d, .after = fdr)

print(p_and_cohen_values)

#write output, will be used in supplement
write.csv(p_and_cohen_values, file = paste0(homedir, "/results/promis_pairwise_p_and_cohen_d_values.csv"), row.names = TRUE)

#save ones that meet correction
pfdr_0.05 <- p_and_cohen_values %>%
  filter(fdr <0.05)

print(pfdr_0.05)

#bonferroni correct
#pbonf <- round(p.adjust(p_values, method = "bonferroni"),3)
#pbonf_0.05 <- pbonf[pbonf < 0.05]
#print(pbonf_0.05)

@@

#### Plots 
##### Box plot no jitter
```{r box_plot_no_jitter}

@@

  "MS+noA" = "#1F968B",
  "MS+mildA" = "#39568C",
  "MS+severeA" = "#482677" 
)

#fade colors at three different fade levels
#custom_colors_faded <- addFade(col = custom_colors, fade = c(0.1, 0.5, 1))

#change fill colors with progressive fades
#custom_color_fill <- c(
#  custom_colors_faded[1,1],
#  custom_colors_faded[2,2],
#  custom_colors_faded[3,3] 
#)

##### BOX PLOT NO JITTER
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.65, outlier.size = 0, linewidth=0.8, width = 0.5) +  # Add boxplots with some transparency
  scale_color_manual(values = custom_colors) +  # Apply custom color scale
  scale_fill_manual(values = custom_colors) +  # Apply custom fill scale
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    aspect.ratio = 7/6,
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

@@

@@
